---
title: 'A Systematic Literature Review'
output:
  pdf_document: default
  html_document:
    df_print: paged
  html_notebook: default
  word_document: default
---
This was developed with bib2df version 1.1.1, installation instructions available [here][1], 
and one example [here][2]. Github project is available [here][3]

[1]: https://docs.ropensci.org/bib2df/
[2]: https://docs.ropensci.org/bib2df/articles/bib2df.html
[3]: https://github.com/ropensci/bib2df

Is better to confirm that the files are in UTF-8 encoding. 
The bibtex files must be checked. There should be spaces between "=":
```
@Article{Binmore2008,
  Title = {Do Conventions Need to Be Common Knowledge?},
  Author = {Binmore, Ken},
  Journal = {Topoi},
  Year = {2008},
  Number = {1},
  Pages = {17--27},
  Volume = {27}
}
```
This code correct that:
```
tx<-readLines(file)
tx2<-gsub(pattern = "=\\{",replacement = " = {",x = tx)
writeLines(text = tx2,con = 'corrected_scopus.bib')

```

# Import Libraries

```{r message=FALSE, warning=FALSE}
# Setup library
library(bib2df)
library(bibtex)
library(tibble)
library(dplyr)

#setwd('C:/nuvem/Dropbox/doutoramento/tese/SLRDropout/analysis')
```

List all the files with bib extension
```{r}
# Define the folder where the .bib files are located
bib_files_path <- "./articles"

# Get a list of all .bib files in the directory
bib_files <- list.files(path = bib_files_path, pattern = "ScienceDirect.*\\.bib$", full.names = TRUE)

# Initialize an empty data frame to store the merged data
science <- NULL

# Loop through each .bib file, process it, and merge it
for (file in bib_files) {
  # Read the .bib file into a data frame
  science_data <- bib2df(file = file)
  
  # Print the dimensions of the current file's data
  print(paste("Processing file:", file))
  print(dim(science_data))
  
  # Merge the current data frame with the main data frame
  if (is.null(science)) {
    science <- science_data
  } else {
    science <- rbind(science, science_data)
  }
}

# Print the final dimensions of the merged data
print("Final dimensions of the merged data:")
print(dim(science))
```
Output
```{r}
names(science)
science
```

Artigos sem abstracts

```{r}
dim(science)

science %>% filter(is.na(ABSTRACT)) %>% select(TITLE,URL,ABSTRACT,URL,DOI)

```
Artigos com abstracts

```{r}
dim(science)

science %>% filter(!is.na(ABSTRACT)) %>% select(TITLE,URL,ABSTRACT,URL,DOI)

```

Vamos utilizar o bibliometrix

* AU: Authors
* TI: Document Title
* SO: Publication Name (or Source)
* JI: ISO Source Abbreviation
* DT: Document Type
* DE: Authors' Keywords
* ID: Keywords associated by SCOPUS or WoS database
* AB: Abstract
* C1: Author Address
* RP: Reprint Address
* CR: Cited References
* TC: Times Cited
* PY: Year
* SC: Subject Category
* UT: Unique Article Identifier
* DB: Database


```{r}
# Load necessary library
library(bibliometrix)

# Define the folder containing the .bib files
bib_files_path <- "./articles"

# Get a list of all .bib files in the directory
bib_files <- list.files(path = bib_files_path, pattern = "\\.bib$", full.names = TRUE)

# Initialize an empty list to store data frames
data_list <- list()

# Loop through each .bib file
for (file in bib_files) {
  print(paste("Processing file:", file)) # Display progress
  
  # Read the .bib file using bibliometrix
  science_data <- convert2df(file = file, dbsource = "scopus", format = "bibtex")
  
  # Display dimensions of the current file's data
  print(dim(science_data))
  
  # Append the data to the list
  data_list[[file]] <- science_data
}

# Standardize column names across all data frames
common_cols <- Reduce(intersect, lapply(data_list, colnames))

# Retain only the common columns and combine data frames
merged_data <- do.call(rbind, lapply(data_list, function(df) df[, common_cols]))

# Display the dimensions of the final merged dataset
print("Final dataset dimensions:")
print(dim(merged_data))

# View a preview of the data
head(merged_data)

```


```{r}
results <- biblioAnalysis(merged_data, sep = ";")
options(width=100)
S <- summary(object = results, k = 10, pause = FALSE)
```

```{r fig.height=10, fig.width=20}
plot(x = results, k = 10, pause = FALSE)
```


Artigos mais citados
```{r}
CR <- citations(merged_data, field = "article", sep = ";")
cbind(CR$Cited[1:10])
```

```{r}
CR <- localCitations(merged_data, sep = ";")
CR$Authors[1:10,]
```

```{r}
DF <- dominance(results, k = 10)
DF
```


```{r}
topAU <- authorProdOverTime(merged_data, k = 10, graph = TRUE)
```

Mais informações sobre o bibliometrix e exemplos [aqui](https://www.bibliometrix.org/vignettes/Introduction_to_bibliometrix.html)
